% Created 2017-06-23 Fri 04:38
% Intended LaTeX compiler: pdflatex
\documentclass[11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{grffile}
\usepackage{longtable}
\usepackage{wrapfig}
\usepackage{rotating}
\usepackage[normalem]{ulem}
\usepackage{booktabs}
\usepackage{amsmath}
\usepackage{textcomp}
\usepackage{amssymb}
\usepackage{capt-of}
\usepackage{hyperref}
\author{Kadin Buckton}
\date{\today}
\title{Portfolio}
\hypersetup{
 pdfauthor={Kadin Buckton},
 pdftitle={Portfolio},
 pdfkeywords={},
 pdfsubject={},
 pdfcreator={Emacs 25.1.1 (Org mode 9.0.6)}, 
 pdflang={English}}
\begin{document}

\maketitle
\section*{Self and Others}
\label{sec:orgc7459c6}
\subsection*{Who am I?}
\label{sec:orgcdb7af8}
\subsubsection*{Brief Biography}
\label{sec:org47cdbf3}
\begin{itemize}
\item Family Members
\label{sec:orgbac0735}
\begin{itemize}
\item Immediate Family
\label{sec:orgfcb92d8}
\begin{itemize}
\item Living with me
\label{sec:org8af0241}
\begin{itemize}
\item Mother
\label{sec:org2f80489}
Krista Parker
\item Stepfather
\label{sec:org26bf957}
Jeremy Yourchuk
\item Brother
\label{sec:org98c27e5}
Kyran Parker
\end{itemize}
\item Living with dad
\label{sec:org4e1188a}
\begin{itemize}
\item Stepmother
\label{sec:org5cfbfdb}
Louise Roy
\item Father
\label{sec:orgf5f9b24}
Christopher Buckton
\item Brothers
\label{sec:orgcfd3f2c}
Noah, Nathen and Nolan Buckton-Roy
\end{itemize}
\end{itemize}
\end{itemize}
\item Friends
\label{sec:org2cab917}
\begin{itemize}
\item Alexander Morin
\label{sec:org51de1d1}
My best friend, do everything together
\end{itemize}
\item Girlfriend
\label{sec:org2e6e87c}
\begin{itemize}
\item Liliana Rhein
\label{sec:orgd132777}
Been together for roughly three years. Plan on living together after College/University
\end{itemize}
\item Pets
\label{sec:orgeb91d73}
\begin{itemize}
\item Living with me
\label{sec:org2a6c2e0}
\begin{itemize}
\item Dogs
\label{sec:org5255e01}
Kiara and Kazer. Kiara is a female yellow lab with infinite energy. Once swam across the haviland lake without breaking a sweat, had to be picked up in a canoe. Kazer is a male black lab, a little more relaxed than his girlfriend. Was attacked by another dog, puncturing his back and injuring his knee. Recovered well, and is back to running around, albeit a little slower than Kiara.
\item Cat
\label{sec:orgd83410a}
We originally had two cats, Toby and Kya. Toby ended up running off one day and never came back. Kya is a black/grey cat, very cuddly. Will sleep on you if you let her.
\end{itemize}
\item Living with dad
\label{sec:orgea62e4e}
\begin{itemize}
\item Dogs
\label{sec:orgc398732}
Two little Shiatsu/Pomeranian mixes, both female, love to lick peoples faces. When shaved, they look like little teddy bears.
\item Bearded Dragons
\label{sec:org49b5db3}
Originally we had 1, then another, then another until we ended up with 5 of these funny lizards. Unfortunately, Louise found out that she was allergic to them and was forced to give 3 of them away. Now only the original (little buddy, who isn't very little anymore) and Kevin (the angry one, only lets me pet him some days) remain. Love baths and running around chasing the dogs.
\item Fish
\label{sec:orgfb43599}
I don't think any of the fish actually have names. Nathen has a beta fish, and there is a tank of misc. fish in the living room. They are fun to look at, and serve as occasional food for the next pet on the list
\item Turtle
\label{sec:orgd44987d}
Our turtle, who happens to be named Turtle, spends most of his day under his basking lamp. However when he's not basking, he's swimming around chasing fish, and looking at you as you walk by his tank.
\end{itemize}
\end{itemize}
\item Schools Attended
\label{sec:org7c6c3ad}
\begin{itemize}
\item Greenwood Elementary School
\label{sec:orga455e61}
Attended from JK to Grade 6. Enjoyed (most) of my time there, good teachers. Still talk to my Grade 6 teacher (Mrs. Wilcox) sometimes whenever I pop in to say hello. Moved to the Korah 7/8 program the first year it was created, half to escape the bullying that had started and half for the computer labs. 
\item Korah Collegiate and Vocational School
\label{sec:orgf8e1ed9}
Have been attending Korah since Grade 7. Currently enrolled, this semester taking Foods, Personal Life Management, Advanced Functions and Computer Science. In fact, this is actually an exam for my Personal Life Management class, don't tell anybody! Teachers here are great, (most of) the people are super nice, and I met my best friend (Alex) in grade 7 here.
\end{itemize}
\item Sports
\label{sec:org7df9711}
I've tried most sports; Soccer, Baseball, Football, Badminton, however the only sport that really ever stuck was Hockey. Started when I was a kid, and I've been playing ever since. Next year is my last year, excepting College/University hockey. Hopefully going into Midget AA, will have to see how I do in drafts.
\item Personality Traits
\label{sec:org9a9835f}
\begin{itemize}
\item Good at analyzing situations
\item Quiet / Introverted
\item Don't like having a schedule
\item Curious / Inquisitive
\end{itemize}
\item Hobbies
\label{sec:org4a6b5a9}
Some of my hobbies include; Computer Programming, Hockey, Video Gaming, Biking, and Hiking.
\item Post Secondary Plans
\label{sec:org433e800}
Currently up in the air about this, was planning for a while to go into the Computer Science course at Algoma U, but recently have been exploring the Computer Security field as a future career. Will most likely either go to Algoma University or Sault College, for the fact that it is cheaper to remain in the city rather than go somewhere else for my post secondary.
\end{itemize}
\subsubsection*{Famous Quote or Proverb that describes my personality and/or outlook on life}
\label{sec:org5235c1a}
\begin{quote}
Do not take life too seriously. You will never get out of it alive. --Elbert Hubbard
\end{quote}
This quote describes my outlook on life fairly well. Take things as they come, and it helps me remember that whatever happens today, it will seem inconsequential in a few years so why should I stress over it?
\subsection*{Resources}
\label{sec:org646a368}
\subsubsection*{Human Resources in my life}
\label{sec:org1f25e0e}
\begin{itemize}
\item Liliana
\label{sec:org3214a1a}
\begin{itemize}
\item How do you know them?
\label{sec:org307dc32}
She's my girlfriend, for 3 years.
\item How do they help you?
\label{sec:org05a9ec2}
She reminds me every day that there are people that care about me, and inspires me to achieve any goal that I set for myself.
\item How do you get ahold of them?
\label{sec:orge63df8a}
I call her. On the telephone. Or over the internet.
\end{itemize}
\item Alexander Morin
\label{sec:org6d8bdca}
\begin{itemize}
\item How do you know them?
\label{sec:org7ad8f51}
I've known him ever since grade 7, when I moved here (Korah) for the 7/8 program. Since then we've been (mostly) inseparable, playing video games and just hanging out. I also occasionally scribe for him, because he has dyslexia, and finds it very hard to write.
\item How do they help you?
\label{sec:orgd29d330}
He helps me remember to relax sometimes, unwind over a barbecue together and helps me focus on what I want to do in life.
\item How do you get ahold of them?
\label{sec:org43f61fb}
Talk to him at school, or call him. On the telephone. Or over the internet.
\end{itemize}
\end{itemize}
\subsubsection*{Personal Resources}
\label{sec:orgebf9764}
\begin{itemize}
\item Skills
\label{sec:org8b0e4c1}
\begin{itemize}
\item Adept at technology
\item Strategist
\item Intelligent
\item Management
\end{itemize}
\item Interests
\label{sec:org704a557}
\begin{itemize}
\item Coding
\item Video Games
\item Books
\item Music
\item Cool Creepy Things
\end{itemize}
\item Health/Fitness
\label{sec:org0e16f09}
Reasonably fit, can lift 140+ lbs, which is almost my body weight, which is 164 lbs. At 5'11, this gives me a BMI of 22, or with the newer SBMI, 37/70. Both of which are in the healthy range. This is going to help me as I work towards independence because I wont have to worry about increased health risks, and can do more without becoming fatigued.
\end{itemize}
\subsection*{Goals}
\label{sec:org9e8fe2d}
\subsubsection*{Identify and explain 2 short term goals (one year or less)}
\label{sec:org1fcc202}
\begin{itemize}
\item Get more physically fit
\label{sec:org0e961f6}
\item Save up some money
\label{sec:org35af02e}
\end{itemize}
\subsubsection*{Identify and explain 1 long term goal (one year or longer) and create a SMART goal plan for it}
\label{sec:org64bf688}
\begin{itemize}
\item 
\label{sec:org22283db}
\end{itemize}
\subsubsection*{Describe the lifestyle you hope to have when you're 30 years old}
\label{sec:orgc52dc76}
\begin{itemize}
\item City
\label{sec:orgb6c323c}
Phoenix, Arizona
\item Home
\label{sec:orgec76b2c}
Doesn't really matter, as long as it has a pool.
\item Job
\label{sec:org890b11f}
Something in the Computer Security field.
\item Family
\label{sec:org3ad959b}
Liliana Rhein, Single Child, preferably a boy (don't tell Lili I said that).
\item Vehicle
\label{sec:org97cb1e8}
A black Impala.
\item Pets
\label{sec:org6587e4b}
A Corgi, Lizards, and a Pacman Frog.
\item Finances
\label{sec:org44a0a0b}
Something around 75k\$ a year for myself.
\end{itemize}
\subsection*{Communication}
\label{sec:orgd9f983c}
\subsubsection*{Overview of your oral communication ability as it relates to conversing with both people you know, as well as people you do not know}
\label{sec:org36d015d}
\begin{itemize}
\item People you know
\label{sec:orgc004411}
\item People you don't know
\label{sec:orge7daa62}
\item Styles of communication I use
\label{sec:orgf085a7b}
\end{itemize}
\subsubsection*{Explain the process of active listening and describe your personal level of competency}
\label{sec:org9f7b218}
\begin{itemize}
\item In the classroom
\label{sec:orge7fb14a}
\item With peers
\label{sec:org6f5bf20}
\end{itemize}
\subsubsection*{Comment on how aware you and confident you are of your non-verbal communication}
\label{sec:org1a04f1d}
\begin{itemize}
\item Body language
\label{sec:orgb2c6189}
\item Nervous habits
\label{sec:org8e403b1}
\item Eye contact
\label{sec:org37de989}
\item Personal space
\label{sec:orgadc63aa}
\item Image projection
\label{sec:org01098c7}
\end{itemize}
\subsection*{Time Management and Productivity}
\label{sec:org611f2c6}
\subsubsection*{Identify and briefly describe 3 time wasters that you personally experience and know you need to manage better}
\label{sec:org5bb63c5}
\subsubsection*{Identify and explain one strategy you could implement to be more productive with your time}
\label{sec:org87445dd}
\section*{Pathways}
\label{sec:org6605206}
\subsection*{Career/Job Goals(s)}
\label{sec:orge21c357}
\subsubsection*{Identify and describe a job you would like to have one day and why you would like that job}
\label{sec:org570fd3c}
A job I would like to have one day is to be an Information Security Analyst. I'd like that job because it involves monitoring networks for security breaches, conduct testing to determine whether or not there are any security holes in a system, and help plan and conduct security procedures.
\subsubsection*{Describe specifically what education, skills, and personal attributes you will need to do that job}
\label{sec:org1c17328}
Typically a Bachelor's Degree is required, along with related experience in the same field. Some skills needed include analytical skills, the need to be detail oriented, have problem solving skills and ingenuity. 
\subsection*{Job Search and Interview Preparation}
\label{sec:org6b36eaf}
\subsubsection*{Identify some different ways people go about finding jobs and describe how you (or a friend/parent/sibling) found their job}
\label{sec:org4da5733}
I don't have any siblings or friends with jobs, so I can't speak for that part. Some of the ways people go about finding jobs, however, I can speak for.
\begin{itemize}
\item Online
\label{sec:orged8be26}
A (relatively) newer way of finding jobs involves the internet. Recruiters, who are people looking for people looking for jobs, post job openings on different websites, with descriptions, salaries, benefits, and any other information one might want. Then, someone looking for a job can go to these websites, and submit resumes either online or in person (by going to the store that is hiring), which brings me to the next way.
\item In-Person
\label{sec:org3edc9f3}
Sometimes stores don't have all this fancy internet stuff. In these cases, if one was looking for a job they might see a store with a "We're Hiring" sign in their window. Then this person would go into the store with a resume, and give it to the manager (or whoever handles hiring at the company). This method usually makes you look better than the online method, though I don't have any anecdotal evidence to prove it. 
\item Through a Friend or Family Member
\label{sec:org4d3f801}
Though much rarer than the previous two, sometimes people just get jobs though a friend or family member. A good example of this is a family business. If my mother ran a grocery store, for example, I don't think she would make me submit a resume in order to stock shelves.
\end{itemize}
\subsubsection*{Include an edited version of your resume here}
\label{sec:org8706bf0}
\href{file:///home/kadin/Downloads/Kadin\%20Parker\%20Resume\%20-\%20Any.pdf}{Resume}
\section*{Finance}
\label{sec:orgd9e638a}
\subsection*{Budgeting and Saving}
\label{sec:orgb41b133}
\subsubsection*{Describe what the term "budgeting" means and the importance of budgeting. Include a blank budget table.}
\label{sec:org6fdeb0b}

\subsubsection*{Identify 3 advantages for saving money and reflect personally on how well you save money}
\label{sec:org57d10b7}
\subsection*{Pay Stubs}
\label{sec:org6e05421}
\subsubsection*{Describe the type of information presented on a pay stub}
\label{sec:org79611fd}
\subsubsection*{Explain why it is important to review your pay stubs regularly, and the possible risks of not checking your pay stubs}
\label{sec:org1d1dade}
\subsection*{Credit Cards and Debt}
\label{sec:orgba9d41b}
\subsubsection*{Describe the pros and cons of credit cards and whether or not you wish to have one someday - Why or Why Not?}
\label{sec:orgc36a51d}
\subsection*{Smart Shopping}
\label{sec:orgfda0419}
\subsubsection*{Identify 3 strategies you should use when shopping to ensure you are getting the best deals for your dollars}
\label{sec:org232acae}
\begin{itemize}
\item Coupons
\label{sec:org68793a4}
One of the best ways to save money is to not pay full price on things. There are almost always coupons in stores and online that allow you to save upwards of 30\% on everyday items.
\item Sales
\label{sec:org82664ed}
\item Buying Bulk
\label{sec:orgdafcef0}
\end{itemize}
\subsubsection*{Describe the level of confidence you have in distinguishing your "needs" from your "wants" \emph{and} utilizing strategies to ensure all of your clothing and food needs will be met, once you're living on your own}
\label{sec:orgae48aa0}
If we're using an 'out of 10' system, I would rate my confidence as a solid 10. 
\section*{Community and World}
\label{sec:orga1310c3}
\subsection*{Values}
\label{sec:org6ffbd83}
\subsubsection*{Identify and describe 4 values that you have}
\label{sec:org9b625eb}
\subsubsection*{Comment on how these 4 values influence your decision making}
\label{sec:org5b487f3}
\subsection*{Decision Making}
\label{sec:org83af579}
\subsubsection*{Explain which decision making style you most often use for tough decisions and why you use it}
\label{sec:org7cc6daf}
\subsubsection*{Identify and describe \emph{one} example of a bad decision that you made and which decision making style you used to make it.}
\label{sec:orgce26ce2}
\begin{itemize}
\item Were there any consequences from it that affected you or others?
\label{sec:orgd671648}
\end{itemize}
\subsubsection*{Identify and describe \emph{one} example of a good decision that you made and which decision making style you used to make it.}
\label{sec:org904dd1e}
\begin{itemize}
\item Did this decision affect anyone besides yourself? If so, how?
\label{sec:orga98d96f}
\end{itemize}
\subsection*{World Impact}
\label{sec:orgba0460a}
\subsubsection*{Identify 1 decision you have made that has world impact (may start within the home and reach community or the world). Think of things like purchasing cheap clothing, using antibiotics, recycling, using environmental cleaners, smoking, etc.}
\label{sec:org7834634}
\subsubsection*{Explain how these decisions affect you, people close to the situation, companies or cities/}
\label{sec:org4d74c7a}
\subsection*{Resources}
\label{sec:orga35abd6}
\subsubsection*{Identify 2 community resources you use or may have to use. Include a brief description}
\label{sec:org6cb9b7a}
\section*{Household Management}
\label{sec:orgf33f1c3}
\subsection*{Toxin Free Products}
\label{sec:org7c33eef}
\subsubsection*{Complete a list of 5 products that are common in households that are toxic to us and list a healthy alternative to each one}
\label{sec:orgc7f8f6e}
\subsubsection*{Choose your favorite product and include a recipe to make the product using healthy home ingredients. Include the original product, the recipe, an image and at least 1 potential benefits}
\label{sec:org208ead0}
\end{document}